Pool Model

### 2025-08-28 pool_model.tex
formatting of margins
insert blank abstract on new page
new caption

\setlength{\tabcolsep}{1.3pt}
\usepackage{acronym}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage[
    backend=biber,
    sorting=none,
    style=numeric-comp,
    hyperref=true,
    maxnames=2,
    url=false,
    isbn=false,
    eprint=false,
    date=year,
    doi=false,
    giveninits=true
]{biblatex}
\usepackage{array}
\usepackage{bm}
\usepackage{booktabs}
\usepackage[aboveskip=1pt,labelfont=bf,labelsep=period,justification=raggedright,singlelinecheck=off, font=small]{caption}
\usepackage{color}
\usepackage{ctable} % for \specialrule command
\usepackage{diagbox}
\usepackage{float}
\usepackage[T1]{fontenc}
\usepackage[a4paper,inner=2cm,outer=2cm]{geometry}
\usepackage{graphicx}% Include figure files
\usepackage{here}
\usepackage{hyperref}
\usepackage{lipsum}
\usepackage{listings}
\usepackage{listings-rust}
\usepackage{mathtools}
\usepackage{mathrsfs}
\usepackage{multirow}
\usepackage{newfloat}
\usepackage{siunitx}
\usepackage{subcaption}
\usepackage{tabularx}
\usepackage[dvipsnames]{xcolor}
\usepackage{xpatch}

@@

\tableofcontents

@@

\label{eq:reactions_resource}

@@

\begin{figure}[h]

@@

    1&=& 2\int_0^{t_L} \lambda L(t)e^{\alpha(t_L-t)}dt\\
    1  &=& 2\lambda e^{\alpha t_L}\frac{1-e^{-(\mu+\lambda+\alpha)t_L}}{\mu+\lambda+\alpha}.

@@

    t_L &\approx& -\frac{1}{\alpha}\ln\left(\frac{2\lambda}{\mu+\lambda+\alpha}\right).

@@

\begin{figure}[H]

@@

\begin{figure*}[t!]

@@

    \dot{G}_A &=& \mathcal{B}_A(G_B)G_A\left(1 - \frac{G_A+G_B}{N_t}\right)\\
    \dot{G}_B &=& \mathcal{B}_B(G_A) G_B\left(1-\frac{G_A+G_B}{N_t}\right).
\label{eq:ode_inhib1}

@@

    \mathcal{B}(G)&=&\frac{\alpha}{1+KI(G)},
\label{eq:ode_inhib_B}

@@

    \dot{G}_A &=& \frac{\alpha_A G_A}{1+K_BG_B}\left(1 - \frac{G_A+G_B}{N_t}\right)\\
    \dot{G}_B &=& \frac{\alpha_B G_B}{1+K_AG_A}\left(1-\frac{G_A+G_B}{N_t}\right).
\label{eq:ode_inhib2}

@@

    \dot{G}_A &=&\tilde{\alpha}_A\frac{G_A}{G_B}\left(1 - G_A-G_B\right)\\
    \dot{G}_B &=& \tilde{\alpha}_B\frac{G_B}{G_A}\left(1-G_A-G_B\right).
\label{eq:ode_inhib3}

@@

\label{eq:ode_inhib_psi}

@@

    \psi&=&1:\quad\text{A and B are equivalent}\\
    \psi&>&1:\quad\text{B grows faster/inhibits A}\\
    \psi&<&1:\quad\text{A grows faster/inhibits B}

@@

    % TODO make this into 2x2 grid for plots and insert eqnarray from before as well
    \includegraphics[width=0.9\columnwidth]{Figures/pool_model_1pool_inhib.pdf}

@@

    \dot{G}_A &=& \mathcal{B}_A(P_B,R)G_A\\
    \dot{G}_B &=& \mathcal{B}_B(P_A,R)G_B\\
    \dot{R} &=&-\mathcal{B}_A(P_B,R)G_A-\mathcal{B}_B(P_A,R)G_B\\
    \dot{P}_A &=& \mathcal{F}_A(R,G_A)\\
    \dot{P}_B &=& \mathcal{F}_B(R,G_B).

@@

    \begin{cases}
    \dot{G}_A = P_B G_A\left(1 - G_A-G_B\right)\\
    \dot{G}_B = \psi P_A G_B\left(1 - G_A-G_B\right)\\
    \dot{P}_A = G_A\left(1 - G_A-G_B\right)\\
    \dot{P}_B =\phi G_B\left(1 - G_A-G_B\right)
    \end{cases}.

@@

    \begin{cases}
        \dot{L_A} = -\lambda_A R L_A\\

@@

        \dot{G_B} = \lambda_B R L_B + \frac{\alpha_B}{1 + \mu_I I} R G_B\\
    \end{cases}.

@@

    \begin{cases}
        \dot{R} = -\frac{\alpha_A}{N_t} R G_A-\frac{\alpha_B}{(1 + \mu_I I) N_t} R G_B \\
        \dot{I} = \kappa G_A
    \end{cases}.

@@

        The volume is equally distributed between each new cell and the new positions are picked random but at opposing sides on a circle around the original center of the single cell.

@@

\begin{table*}[h]

@@

    \begin{tabularx}{\columnwidth}{@{}l *3{>{\centering\arraybackslash}X}@{}}

@@

@@

% ================================================================================================
\beginsupplement
\section{Supplementary Material}
% ================================================================================================
\subsection{General Mathematical Formalism}  \label{ssec:supplement1}
Consider the system consisting of $N$ species in $M$ different states.
In the general representation, all discussed in the main part systems  can be described with the Ordinary Differential Equations (\acp{ode}) using a non-linear function $\mbF$:
\begin{equation}
   \dot{\mbx} = \mbF(\mbx, \mbm, \mbp, \mbu),
\label{eq:model_ODE_x}
\end{equation}
where  $\mbx \in \mathbb{R}^{N}  \otimes \mathbb{R}^{M}$ is a vector describing bacterial count.
In matrix form it can be written as
\begin{equation}
    \mbx = \begin{pmatrix}
        x^1_1  & \dots & x^1_N  \\
        \vdots &       & \vdots \\
        x^M_1  & \dots & x^M_N  \\
            \end{pmatrix}
    \label{eq:model_bact}
\end{equation}
with $x_{j}^{i}$ describing the bacterial counts for species $i$ in state $j$.
$\mbu$ is the vector of different inputs of the model, e.g., temperature, pressure etc.
The vector $\mbm \in \mathbb{R}^{K}$ includes all variables corresponding to the microenvironment of the system which can be concentration of the inhibitors or activators:
\begin{equation}
    \dot{\mbm} = \mbH (\mbx, \mbm, \mbp, \mbu).
    \label{eq:model_microenv}
\end{equation}
Here function $\mbH$ is in general case also non-linear.\\
%
The advantage of the following formulation is its generality.
Depending on the knowledge about the system as well as the needed level of accuracy one can define an arbitrary number of states $M$ and control the complexity of the model.
Moreover, opposite to the already known Predictive Microbiology like Baranyi and Roberts one can easily change.\\
%
To calculate the bacterial count for one species $i$, we simply need to sum the tensor/vector $\mbx$ over all possible states:
\begin{equation}
    N_i = \sum_k \mbx_i^k.
\label{eq:N_pro_species}
\end{equation}
While the total bacterial count of all species of our system is
\begin{equation}
    N = \sum_i \sum_k \mbx_i^k.
\label{eq:N_total}
\end{equation}
%
%
%The three pool system described with equations~\ref{eq:ode_3pools} will be written as
%\begin{equation}
%    \dot \mbx  = A \mbx, \hspace{3mm} A = \begin{pmatrix}
%        -(\mu + \lambda) & 0             & 0      \\
%        \lambda          & \alpha - \mu' & 0      \\
%        \mu              & \mu'          & -\beta 
%    \end{pmatrix}.
%\label{eq:x_repres_3pools}
%\end{equation}
%
Using such matrix representation of the bacterial system, we can rewrite, for example, the three-pool model with limiting resource described with equations~\ref{eq:ode_3pool_resource} in a more compact form.
The concentrations of the pools are then the components of our variable vector $\mbx (t) = (L(t), G(t), D(t))^T$.
%
\begin{eqnarray}
    \dot \mbx  &=& \mbF(\mbx, \mbm, \mbp, \mbu) = \begin{pmatrix}
        -(\mu + \lambda) & 0               & 0      \\
        \lambda          & \alpha R - \mu' & 0      \\
        \mu              & \mu'            & -\beta 
    \end{pmatrix} \mbx\\
    \dot \mbm &=& \mbH (\mbx, \mbm, \mbp, \mbu) = -\frac{\alpha}{N_t} R G.
\label{eq:x_repres_3pools_resource}
\end{eqnarray}
Separating linear and non-linear parts in two terms yields
\begin{equation}
    \dot \mbx = \begin{pmatrix}
        -(\mu + \lambda) & 0       & 0 \\
         \lambda         & \alpha  & 0 \\
         \mu &  \mu'& - \beta 
    \end{pmatrix} 
    \mbx + \frac{\alpha}{N_t} x^2 \sum_i^3 x^i \begin{pmatrix} 0 \\ 1 \\ 0  \end{pmatrix}.
\label{eq:x_repres_3pools_resource2}
\end{equation}
Here the first term is the linear part and the second term define the quadratic behavior of the system.
%
\paragraph{Generalized Lotka-Volterra}

@@

\begin{table}[H]
    \centering
    \begin{tabularx}{\textwidth}{@{}l *2{>{\centering\arraybackslash}X} l *2{>{\centering\arraybackslash}X}@{}}
        \multicolumn{3}{c}{\textbf{\acs{ode}}} & \multicolumn{3}{c}{\textbf{\acs{abm}}}\\
        \toprule
        \multicolumn{6}{c}{\textbf{Cellular Reactions}}\\
        \toprule
        Production $G_A$            & $\alpha_A$    & $0.002$\unit{\per\minute}
        & Uptake                    & $u_A$         & $0.01$\unit{\per\minute}\\
        Production $G_B$            & $\alpha_B$    & $0.002$\unit{\per\minute}
        & Uptake                    & $u_B$         & $0.01$\unit{\per\minute}\\
        Production $I$              & $\kappa$      & $0.1$\unit{\per\minute}
        & Production $I$            & $b$           & $0.1$\unit{\per\minute}\\
        Inhibition                  & $\mu_I$       & $1.0\cdot 10^{-7}$\unit{\per\micro\metre\cubed}
        &                           & $\nu_I$       & $0.1$\unit{\micro\metre\cubed\per\mol}\\
        &&
        & Conversion                & $\sigma$      & $0.1$\unit{\micro\metre\cubed\per\mol}\\
        Total volume                & $N_t$& $2.0\cdot 10^5$\unit{\micro\metre\cubed}
        &&&\\
        &&
        & Diffusion $R$             & $D_R$         & $30.0$\unit{\micro\metre\squared\per\minute}\\
        &&
        & Diffusion $I$             & $D_I$         & $30.0$\unit{\micro\metre\squared\per\minute}\\
        % Note: this diffusion roughly corresponds to the one of ethanol in water
        % (see https://de.wikipedia.org/wiki/Diffusionskoeffizient#In_Fl%C3%BCssigkeiten)
        % 15.0 µm^2/min = 0.9 m^2/s
        % Ethanol: 0.84 m^2/s
        \toprule
        \multicolumn{6}{c}{\textbf{Physical Mechanics \& Interactions}}\\
        \toprule
        &&& Damping                 & $\eta$        & $0.5$\unit{\per\minute}\\
        &&& Mass                    & $m$           & $7.70$\unit{\pico\gram}\\
        &&& Potential               & $\epsilon$    & $0.5$\unit{\pico\gram\micro\metre\per\minute\squared}\\
        \toprule
        \multicolumn{6}{c}{\textbf{Cell Cycle}}\\
        \toprule
        Rate $L_A\rightarrow G_A$   & $\lambda_A$   & $0.0025$\unit{\per\minute}
        &                           & $\lambda_A$   & $0.0025$\unit{\per\minute}\\
        Rate $L_B\rightarrow G_B$   & $\lambda_B$   & $0.0005$\unit{\per\minute}
        &                           & $\lambda_B$   & $0.0005$\unit{\per\minute}\\
        &&& Division Vol.           & $V_t$         & $14.14$\unit{\micro\metre\cubed}\\
        \toprule
        \multicolumn{6}{c}{\textbf{Initial Values}}\\
        \toprule
        Volume of $L_A$             & $L_A$         & $127.2$\unit{\micro\metre\cubed}
        & Cell Number               & $C_A$         & 18\\
        Volume of $G_A$             & $G_A$         & $0.0$\unit{\micro\metre\cubed}
        & Cell Volume               & $V_{c,A}$     & $7.07$\unit{\micro\metre\cubed}\\
        Volume of $L_B$             & $L_B$         & $127.23$\unit{\micro\metre\cubed}
        & Cell Number               & $C_B$         & 18\\
        Volume of $G_B$             & $G_B$         & $0.0$\unit{\micro\metre\cubed}
        & Cell Volume               & $V_{c,B}$     & $7.07$\unit{\micro\metre\cubed}\\
        Relative Nutrients          & $R$         & $1.0$
        & Nutrients                 & $[R_0]$       & $1.0$\unit{\mol\per\micro\metre\cubed}\\
        Inhibitor                   & $I_0$         & $0.0$\unit{\mol}
        & Inhibitor                 & $[I_0]$       & $0.0$\unit{\mol\per\micro\metre\cubed}\\
        \bottomrule
    \end{tabularx}
    \caption{
        Comparison of the parameters for the \ac{ode} model and \ac{abm}.
        % To view, how these parameters are stored inside a cell-agent, we refer to the supplementary
        % material~\ref{sec:supplement-full-parameters}.
    }
    \label{tab:spatial_limit_init}
\end{table}

>>>>

\setlength{\tabcolsep}{1.3pt}
\setlength{\columnsep}{0.4cm}
\usepackage{acronym}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage[
    backend=biber,
    sorting=none,
    style=numeric-comp,
    hyperref=true,
    maxnames=2,
    url=false,
    isbn=false,
    eprint=false,
    date=year,
    doi=false,
    giveninits=true
]{biblatex}
\usepackage{array}
\usepackage{bm}
\usepackage{booktabs}
\usepackage[aboveskip=1pt,labelfont=bf,labelsep=period,justification=raggedright,singlelinecheck=off, font=small]{caption}
\usepackage{color}
\usepackage{ctable} % for \specialrule command
\usepackage{diagbox}
\usepackage{float}
\usepackage[T1]{fontenc}
\usepackage[a4paper,inner=2cm,outer=2cm,top=2.5cm,bottom=2.5cm]{geometry}
\usepackage{graphicx}% Include figure files
\usepackage{here}
\usepackage{hyperref}
\usepackage{lipsum}
\usepackage{listings}
\usepackage{listings-rust}
\usepackage{mathtools}
\usepackage{mathrsfs}
\usepackage{multirow}
\usepackage{newfloat}
\usepackage{siunitx}
\usepackage{subcaption}
\usepackage{tabularx}
\usepackage[dvipsnames]{xcolor}
\usepackage{xpatch}

@@

\begin{abstract}
    TODO
\end{abstract}

\newpage
\tableofcontents

@@

@@

@@

    1&= 2\int_0^{t_L} \lambda L(t)e^{\alpha(t_L-t)}dt\\
    1  &= 2\lambda e^{\alpha t_L}\frac{1-e^{-(\mu+\lambda+\alpha)t_L}}{\mu+\lambda+\alpha}.

@@

    t_L &\approx -\frac{1}{\alpha}\ln\left(\frac{2\lambda}{\mu+\lambda+\alpha}\right).

@@

@@

@@

    \dot{G}_A &= \mathcal{B}_A(G_B)G_A\left(1 - \frac{G_A+G_B}{N_t}\right)\\
    \dot{G}_B &= \mathcal{B}_B(G_A) G_B\left(1-\frac{G_A+G_B}{N_t}\right).

@@

    \mathcal{B}(G) = \frac{\alpha}{1+KI(G)},

@@

    \dot{G}_A &= \frac{\alpha_A G_A}{1+K_BG_B}\left(1 - \frac{G_A+G_B}{N_t}\right)\\
    \dot{G}_B &= \frac{\alpha_B G_B}{1+K_AG_A}\left(1-\frac{G_A+G_B}{N_t}\right).
\end{split}\end{align}

@@

    \dot{G}_A &=\tilde{\alpha}_A\frac{G_A}{G_B}\left(1 - G_A-G_B\right)\\
    \dot{G}_B &= \tilde{\alpha}_B\frac{G_B}{G_A}\left(1 - G_A-G_B\right).
\end{split}\end{align}

@@

@@

    \psi&=1:\quad\text{A and B are equivalent}\\
    \psi&>1:\quad\text{B grows faster/inhibits A}\\
    \psi&<1:\quad\text{A grows faster/inhibits B}

@@

    % TODO make this into 2x2 grid for plots and insert cases for psi from before as well
    \includegraphics[width=\columnwidth]{Figures/pool_model_1pool_inhib.pdf}

@@

    \dot{G}_A &= \mathcal{B}_A(P_B,R)G_A\\
    \dot{G}_B &= \mathcal{B}_B(P_A,R)G_B\\
    \dot{R} &=-\mathcal{B}_A(P_B,R)G_A-\mathcal{B}_B(P_A,R)G_B\\
    \dot{P}_A &= \mathcal{F}_A(R,G_A)\\
    \dot{P}_B &= \mathcal{F}_B(R,G_B).

@@

    \dot{G}_A &= P_B G_A\left(1 - G_A-G_B\right)\\
    \dot{G}_B &= \psi P_A G_B\left(1 - G_A-G_B\right)\\
    \dot{P}_A &= G_A\left(1 - G_A-G_B\right)\\
    \dot{P}_B &=\phi G_B\left(1 - G_A-G_B\right).

@@

@@

    \dot{G_B} = \lambda_B R L_B + \frac{\alpha_B}{1 + \mu_I I} R G_B

@@

@@

        The volume is equally distributed between the two cells and the new positions are picked
        random but at opposing sides on a circle around the original center of the single cell.

@@

\begin{table*}

@@

    \begin{tabularx}{0.8\textwidth}{@{}l *3{>{\centering\arraybackslash}X}@{}}

@@

    \caption{Mappings between \ac{ode} and \ac{abm} parameters.}

@@

% ================================================================================================
\newpage
\beginsupplement
\section{Supplementary Material}
% ================================================================================================
\subsection{General Mathematical Formalism}  \label{ssec:supplement1}
Consider the system consisting of $N$ species in $M$ different states.
In the general representation, all discussed in the main part systems  can be described with the Ordinary Differential Equations (\acp{ode}) using a non-linear function $\mbF$:
\begin{equation}
   \dot{\mbx} = \mbF(\mbx, \mbm, \mbp, \mbu),
\label{eq:model_ODE_x}
\end{equation}
where  $\mbx \in \mathbb{R}^{N}  \otimes \mathbb{R}^{M}$ is a vector describing bacterial count.
In matrix form it can be written as
\begin{equation}
    \mbx = \begin{pmatrix}
        x^1_1  & \dots & x^1_N  \\
        \vdots &       & \vdots \\
        x^M_1  & \dots & x^M_N  \\
            \end{pmatrix}
    \label{eq:model_bact}
\end{equation}
with $x_{j}^{i}$ describing the bacterial counts for species $i$ in state $j$.
$\mbu$ is the vector of different inputs of the model, e.g., temperature, pressure etc.
The vector $\mbm \in \mathbb{R}^{K}$ includes all variables corresponding to the microenvironment of the system which can be concentration of the inhibitors or activators:
\begin{equation}
    \dot{\mbm} = \mbH (\mbx, \mbm, \mbp, \mbu).
    \label{eq:model_microenv}
\end{equation}
Here function $\mbH$ is in general case also non-linear.\\
%
The advantage of the following formulation is its generality.
Depending on the knowledge about the system as well as the needed level of accuracy one can define an arbitrary number of states $M$ and control the complexity of the model.
Moreover, opposite to the already known Predictive Microbiology like Baranyi and Roberts one can easily change.\\
%
To calculate the bacterial count for one species $i$, we simply need to sum the tensor/vector $\mbx$ over all possible states:
\begin{equation}
    N_i = \sum_k \mbx_i^k.
\label{eq:N_pro_species}
\end{equation}
While the total bacterial count of all species of our system is
\begin{equation}
    N = \sum_i \sum_k \mbx_i^k.
\label{eq:N_total}
\end{equation}
%
%
%The three pool system described with equations~\ref{eq:ode_3pools} will be written as
%\begin{equation}
%    \dot \mbx  = A \mbx, \hspace{3mm} A = \begin{pmatrix}
%        -(\mu + \lambda) & 0             & 0      \\
%        \lambda          & \alpha - \mu' & 0      \\
%        \mu              & \mu'          & -\beta 
%    \end{pmatrix}.
%\label{eq:x_repres_3pools}
%\end{equation}
%
Using such matrix representation of the bacterial system, we can rewrite, for example, the three-pool model with limiting resource described with equations~\ref{eq:ode_3pool_resource} in a more compact form.
The concentrations of the pools are then the components of our variable vector $\mbx (t) = (L(t), G(t), D(t))^T$.
%
\begin{align}
    \dot \mbx  &= \mbF(\mbx, \mbm, \mbp, \mbu) = \begin{pmatrix}
        -(\mu + \lambda) & 0               & 0      \\
        \lambda          & \alpha R - \mu' & 0      \\
        \mu              & \mu'            & -\beta 
    \end{pmatrix} \mbx\\
    \dot \mbm &= \mbH (\mbx, \mbm, \mbp, \mbu) = -\frac{\alpha}{N_t} R G.
\end{align}
Separating linear and non-linear parts in two terms yields
\begin{equation}
    \dot \mbx = \begin{pmatrix}
        -(\mu + \lambda) & 0       & 0 \\
         \lambda         & \alpha  & 0 \\
         \mu &  \mu'& - \beta 
    \end{pmatrix} 
    \mbx + \frac{\alpha}{N_t} x^2 \sum_i^3 x^i \begin{pmatrix} 0 \\ 1 \\ 0  \end{pmatrix}.
\label{eq:x_repres_3pools_resource2}
\end{equation}
Here the first term is the linear part and the second term define the quadratic behavior of the system.
%
\paragraph{Generalized Lotka-Volterra}

@@

\begin{table}
    \centering
    \begin{tabularx}{\textwidth}{@{}l *2{>{\centering\arraybackslash}X} l *2{>{\centering\arraybackslash}X}@{}}
        \multicolumn{3}{c}{\textbf{\acs{ode}}} & \multicolumn{3}{c}{\textbf{\acs{abm}}}\\
        \toprule
        \multicolumn{6}{c}{\textbf{Cellular Reactions}}\\
        \toprule
        Production $G_A$            & $\alpha_A$    & $0.002$\unit{\per\minute}
        & Uptake                    & $u_A$         & $0.01$\unit{\per\minute}\\
        Production $G_B$            & $\alpha_B$    & $0.002$\unit{\per\minute}
        & Uptake                    & $u_B$         & $0.01$\unit{\per\minute}\\
        Production $I$              & $\kappa$      & $0.1$\unit{\per\minute}
        & Production $I$            & $b$           & $0.1$\unit{\per\minute}\\
        Inhibition                  & $\mu_I$       & $1.0\cdot 10^{-7}$\unit{\per\micro\metre\cubed}
        &                           & $\nu_I$       & $0.1$\unit{\micro\metre\cubed\per\mol}\\
        &&
        & Conversion                & $\sigma$      & $0.1$\unit{\micro\metre\cubed\per\mol}\\
        Total volume                & $N_t$& $2.0\cdot 10^5$\unit{\micro\metre\cubed}
        &&&\\
        &&
        & Diffusion $R$             & $D_R$         & $30.0$\unit{\micro\metre\squared\per\minute}\\
        &&
        & Diffusion $I$             & $D_I$         & $30.0$\unit{\micro\metre\squared\per\minute}\\
        % Note: this diffusion roughly corresponds to the one of ethanol in water
        % (see https://de.wikipedia.org/wiki/Diffusionskoeffizient#In_Fl%C3%BCssigkeiten)
        % 15.0 µm^2/min = 0.9 m^2/s
        % Ethanol: 0.84 m^2/s
        \toprule
        \multicolumn{6}{c}{\textbf{Physical Mechanics \& Interactions}}\\
        \toprule
        &&& Damping                 & $\eta$        & $0.5$\unit{\per\minute}\\
        &&& Mass                    & $m$           & $7.70$\unit{\pico\gram}\\
        &&& Potential               & $\epsilon$    & $0.5$\unit{\pico\gram\micro\metre\per\minute\squared}\\
        \toprule
        \multicolumn{6}{c}{\textbf{Cell Cycle}}\\
        \toprule
        Rate $L_A\rightarrow G_A$   & $\lambda_A$   & $0.0025$\unit{\per\minute}
        &                           & $\lambda_A$   & $0.0025$\unit{\per\minute}\\
        Rate $L_B\rightarrow G_B$   & $\lambda_B$   & $0.0005$\unit{\per\minute}
        &                           & $\lambda_B$   & $0.0005$\unit{\per\minute}\\
        &&& Division Vol.           & $V_t$         & $14.14$\unit{\micro\metre\cubed}\\
        \toprule
        \multicolumn{6}{c}{\textbf{Initial Values}}\\
        \toprule
        Volume of $L_A$             & $L_A$         & $127.2$\unit{\micro\metre\cubed}
        & Cell Number               & $C_A$         & 18\\
        Volume of $G_A$             & $G_A$         & $0.0$\unit{\micro\metre\cubed}
        & Cell Volume               & $V_{c,A}$     & $7.07$\unit{\micro\metre\cubed}\\
        Volume of $L_B$             & $L_B$         & $127.23$\unit{\micro\metre\cubed}
        & Cell Number               & $C_B$         & 18\\
        Volume of $G_B$             & $G_B$         & $0.0$\unit{\micro\metre\cubed}
        & Cell Volume               & $V_{c,B}$     & $7.07$\unit{\micro\metre\cubed}\\
        Relative Nutrients          & $R$         & $1.0$
        & Nutrients                 & $[R_0]$       & $1.0$\unit{\mol\per\micro\metre\cubed}\\
        Inhibitor                   & $I_0$         & $0.0$\unit{\mol}
        & Inhibitor                 & $[I_0]$       & $0.0$\unit{\mol\per\micro\metre\cubed}\\
        \bottomrule
    \end{tabularx}
    \caption{
        Comparison of the parameters for the \ac{ode} model and \ac{abm}.
        % To view, how these parameters are stored inside a cell-agent, we refer to the supplementary
        % material~\ref{sec:supplement-full-parameters}.
    }
    \label{tab:spatial_limit_init}
\end{table}
